ext_risk_copula

### 2019-01-11 ext_risk_copula.Rmd
modified

rlist<-seq(from=5,to=10,by=1)
a<-0.5
b<-1.5
K_e<-((r^(1/b))-1)/a
rc<-((b/(b-1)))^b # critical value of r from monotonic to osc steady state approach transition

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/hassell_ext_risk_local_disp.pdf",heigh=6,width=10)
op<-par(mfrow=c(2,4),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    #cat("r=",r,"\n")
    s<-varying_d(numsims=10000,numsteps =10,numlocs=5,r=r,K=K_e,a=a,b=b,model="hassell",disp_everywhere=F,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend(x=-0.06,y=0.1, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/hassell_ext_risk_global_disp.pdf",heigh=6,width=10)
op<-par(mfrow=c(2,4),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    #cat("r=",r,"\n")
    s<-varying_d(numsims=10000,numsteps =10,numlocs=5,r=r,K=K_e,a=a,b=b,model="hassell",disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend(x=-0.06,y=0.1, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

@@

```{r fig_msmith, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)

@@

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/msmith_ext_risk_local_disp.pdf",heigh=6,width=10)
op<-par(mfrow=c(3,4),mar=c(5,4,1,1) + 0.2)
for(b in blist){
    s<-varying_d(numsims=10000,numsteps =10,numlocs=5,r=r,K=K_e,a=a,b=b,model="msmith",disp_everywhere=F,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend(x=-0.06,y=0.4, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
    mtext(paste0("b = ", b))
}
par(op)
dev.off()

# plot for global dispersal in D matrix 
pdf("./Results/ext_risk_copula/msmith_ext_risk_global_disp.pdf",heigh=6,width=10)
op<-par(mfrow=c(3,4),mar=c(5,4,1,1) + 0.2)
for(b in blist){
    s<-varying_d(numsims=10000,numsteps =10,numlocs=5,r=r,K=K_e,a=a,b=b,model="msmith",disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend(x=-0.06,y=0.4, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
    mtext(paste0("b = ", b))
}
par(op)
dev.off()
```

![Effect of non-Normal environmental noise copula on extinction risk after 10 years (Maynard Smith model : a = 0.5, r = 5, bc=1.4) with local dispersion; numlocs=5, numsteps=10, numsims=10000\label{fig_risk_local_disp_msmith}](./Results/ext_risk_copula/msmith_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 10 years (Maynard Smith model : a = 0.5, r=5, bc=1.4) with global dispersion; numlocs=5, numsteps=10, numsims=10000\label{fig_risk_global_disp_msmith}](./Results/ext_risk_copula/msmith_ext_risk_global_disp.pdf){ width=40%, height=40% }

>>>>

rlist<-seq(from=1,to=10,by=1)
a<-0.5
b<-1.5
K_e<-((r^(1/b))-1)/a
rc<-((b/(b-1)))^b # critical value of r from monotonic to osc steady state approach transition

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/hassell_ext_risk_local_disp.pdf",heigh=6,width=10)
op<-par(mfrow=c(3,4),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    #cat("r=",r,"\n")
    s<-varying_d(numsims=10000,numsteps =10,numlocs=5,r=r,K=K_e,a=a,b=b,model="hassell",disp_everywhere=F,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend(x=-0.06,y=0.1, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/hassell_ext_risk_global_disp.pdf",heigh=6,width=10)
op<-par(mfrow=c(3,4),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    #cat("r=",r,"\n")
    s<-varying_d(numsims=10000,numsteps =10,numlocs=5,r=r,K=K_e,a=a,b=b,model="hassell",disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend(x=-0.06,y=0.1, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

@@

```{r fig_msmith_r_vary, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)

rlist<-seq(from=3,to=8,by=1)
b<-1.4
a<-0.5
K_e<-((r-1)^(1/b))/a

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/msmith_ext_risk_local_disp_r_variation.pdf",heigh=6,width=10)
op<-par(mfrow=c(2,3),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    s<-varying_d(numsims=10000,numsteps =10,numlocs=5,r=r,K=K_e,a=a,b=b,model="msmith",disp_everywhere=F,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend(x=-0.06,y=0.4, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# plot for global dispersal in D matrix 
pdf("./Results/ext_risk_copula/msmith_ext_risk_global_disp_r_variation.pdf",heigh=6,width=10)
op<-par(mfrow=c(2,3),mar=c(5,4,1,1) + 0.2)
for(r in rlist){
    s<-varying_d(numsims=10000,numsteps =10,numlocs=5,r=r,K=K_e,a=a,b=b,model="msmith",disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend(x=-0.06,y=0.4, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

![Effect of non-Normal environmental noise copula on extinction risk after 10 years (Maynard Smith model : a = 0.5, b = 1.4, rc=4.5) with local dispersion; numlocs=5, numsteps=10, numsims=10000\label{fig_risk_local_disp_msmith_r_vary}](./Results/ext_risk_copula/msmith_ext_risk_local_disp_r_variation.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 10 years (Maynard Smith model : a = 0.5, b=1.4, rc=4.5) with global dispersion; numlocs=5, numsteps=10, numsims=10000\label{fig_risk_global_disp_msmith_r_vary}](./Results/ext_risk_copula/msmith_ext_risk_global_disp_r_variation.pdf){ width=40%, height=40% }

```{r fig_msmith_b_vary, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)

@@

# plot for local dispersal in D matrix 
pdf("./Results/ext_risk_copula/msmith_ext_risk_local_disp_b_variation.pdf",heigh=6,width=10)
op<-par(mfrow=c(3,4),mar=c(5,4,1,1) + 0.2)
for(b in blist){
    s<-varying_d(numsims=10000,numsteps =10,numlocs=5,r=r,K=K_e,a=a,b=b,model="msmith",disp_everywhere=F,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend(x=-0.06,y=0.4, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
    mtext(paste0("b = ", b))
}
par(op)
dev.off()

# plot for global dispersal in D matrix 
pdf("./Results/ext_risk_copula/msmith_ext_risk_global_disp_b_variation.pdf",heigh=6,width=10)
op<-par(mfrow=c(3,4),mar=c(5,4,1,1) + 0.2)
for(b in blist){
    s<-varying_d(numsims=10000,numsteps =10,numlocs=5,r=r,K=K_e,a=a,b=b,model="msmith",disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend(x=-0.06,y=0.4, c("noise : left","noise : right"), fill=c('red', 'blue'), horiz=T, bty='n')
    mtext(paste0("b = ", b))
}
par(op)
dev.off()
```

![Effect of non-Normal environmental noise copula on extinction risk after 10 years (Maynard Smith model : a = 0.5, r = 5, bc=1.4) with local dispersion; numlocs=5, numsteps=10, numsims=10000\label{fig_risk_local_disp_msmith_b_vary}](./Results/ext_risk_copula/msmith_ext_risk_local_disp_b_variation.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 10 years (Maynard Smith model : a = 0.5, r=5, bc=1.4) with global dispersion; numlocs=5, numsteps=10, numsims=10000\label{fig_risk_global_disp_msmith_b_vary}](./Results/ext_risk_copula/msmith_ext_risk_global_disp_b_variation.pdf){ width=40%, height=40% }
